|

### 2017-11-20 pres/state_ms.Rmd
add slides

---
title: "Resiliencia de *Quercus pyrenaica* a dos eventos de sequía"
author: "Perez-Luque AJ; Gea-Izquierdo G; Zamora R; Bonet FJ"
output: 
  beamer_presentation: 
    template: NULL 
bibliography: ../references.bib
csl: ../nature.csl
---

@@

    * Recuento todos los árboles (dbh > 7.5) dentro de un radio de 10 metros 
    * dbh, altura, distancia árbol focal, rumbo 
    * Índices de competencia dependientes e independientes de la distancia [@GeaIzquierdo2009]

@@

# Dendrochronological methods

>>>>

---
title: |
  Resiliencia de *Quercus pyrenaica* a dos eventos de sequía
author: "Perez-Luque AJ; Gea-Izquierdo G; Zamora R; Bonet FJ"
output: 
  beamer_presentation: 
    template: NULL 
    fig_caption: FALSE
bibliography: ../references.bib
csl: ../nature.csl
---

@@

    * Recuento todos los árboles (dbh > 7.5) dentro de un radio de 10 metros 
    * dbh, altura, distancia árbol focal, rumbo 
    * Índices de competencia dependientes e independientes de la distancia [@GeaIzquierdo2009] 
    * [\textcolor{blue}{Resultados}](https://github.com/ajpelu/qpyr_dendro/blob/master/analysis/analysis_competence.md)

--- 
![](../analysis/analysis_competence_files/figure-markdown_github/competence_sj-1.png){height=300px}
--- 
![](../analysis/analysis_competence_files/figure-markdown_github/competence_ca-1.png){height=300px}
---
# Resilience metrics 
Resistance quantifies the severity of the impact of the disturbance in the year it occurred 
Recovery index (*Rc*) is the ability to recover from disturbance relative to its severity. Recovery  = Postdrought / Drought
Resilience index (*Rs*) is the capacity to reach pre-disturbance performance levels. Resilience = Postdrought / Predrought
Relative Resilience (*RRs*) is the resilience weighted by the severity of the disturbance. Relative Resilience = (Postdrought - Drought) / Predrought

@@
